Adopting agile in the large: motivations, success factors and challenges

### 2013-01-26 tex/article.tex
Spellcheck
Fixed: "confident that search matched majority of relevant material"

\usepackage{calc}      % käytetään laskurien (counter) yhteydessä (tiedot.tex)
\usepackage{natbib}
\usepackage{url}
\usepackage{listings}
\usepackage{hyphenat}

@@

% Strikethrough
\usepackage[normalem]{ulem}

@@

As the preliminary search omitted some of the keywords in Table
\ref{table:searchterms} it yielded a small number of additional matches. The
reason for variance in matches was that many articles had creative titles or the
abstracts and keywords were not informative enough. Because of this, the search
with more restrictive keywords was unable to capture all possible matches.
We are however confident that the search covered the majority of material
relating to agile transformations in large organizations. If a wider search
should be performed, our recommendation is to only regard the facets
\textit{agile methods} and \textit{organizational change}. This would lead to
significantly more matches in the first stage of selecting studies, but the
additional effort is necessary due to the limitations of a keyword search.

@@

The reasons to initiate a change fell into three categories, as summarized in
Table \ref{table:motivations}. The primary reasons for change was a strategical
need to improve the performance of the organization. Especially shortening the
time to market was desired. In many cases the change was started when management
acknowledged problems in the current way of working.

@@

@@

% Pitäs olla done:
% Search kuva on selitetty myös tekstissä.
% Inclusion: viewpoint on the organizational transformation [from plan-driven, tms.]
% Used methods: interfacing with various units present in a large organization
%    --> Developmentin koordinointi
% "Coaching and community" --> selitä myös coaching

>>>>

\usepackage{calc}
\usepackage{natbib}
\usepackage{url}
\usepackage{listings}
\usepackage{hyphenat}

@@

% Strike through
\usepackage[normalem]{ulem}

@@

As the preliminary search omitted some of the keywords in Table
\ref{table:searchterms} it yielded a small number of additional matches. The
reason for variance in matches was that many articles had creative titles or the
abstracts and keywords were not informative enough. Because of this, the search
with more restrictive keywords was unable to capture all possible matches.
If a wider search should be performed, our recommendation is to only regard the
facets \textit{agile methods} and \textit{organizational change}. This would
lead to significantly more matches in the first stage of selecting studies.
In our experience a keyword search will not match the large scale facet, but a
manual semantic analysis of the article meta data is required.

@@

The reasons to initiate a change fell into three categories, as summarized in
Table \ref{table:motivations}. The primary reasons for change was a strategic
need to improve the performance of the organization. Especially shortening the
time to market was desired. In many cases the change was started when management
acknowledged problems in the current way of working.

@@

% Fixed:
% We are however confident that the search covered the majority of material
% relating to agile transformations in large organizations.
%    --> Removed 
%    --> In our experience a keyword search will not match the large scale
%    facet, but a manual semantic analysis of the article meta data is required.

@@

% Should be covered
% Inclusion: viewpoint on the organizational transformation [from plan-driven, tms.]
% Used methods: interfacing with various units present in a large organization
%    --> Coordination of development
